The imprint of global magma oceans on exoplanet demographics

### 2023-01-19 src/tex/ms.tex
remove example plots
add results section on pure radius vs bulk density measurements

\subsection{Statistical power of different mission designs}\label{sec:statpower_missions}
\todo[inline]{show detectability of the runaway greenhouse signature for different mission designs}

        \includegraphics[width=\linewidth]{figures/example_Ndetected_surveys.pdf}
        \caption{
        Detections of magma ocean-bearing planets as a function of magma ocean occurrence for different survey designs.
        }
        \label{fig:example_Ndetected_surveys}
    \end{centering}
\end{figure}

>>>>

\subsection{Statistical power of different mission designs}\label{sec:statpower_missions}
\subsubsection{Additional planet mass measurements}
The situation differs when additional information beyond planet radii is available for the characterized planet population.
Since the planet bulk density $\rho \propto R^{-3}$, the signal is stronger when measured in bulk density instead of radius:
With an optimistic choice of geophysical parameters (see above), the average measured radius change is \SI{+15}{\percent} whereas the average density change is \SI{-33}{\percent}.
Constraining bulk densities requires planetary mass measurements.
We now examine the value of a follow-up campaign to constrain planet masses with respect to the detectability of the runaway greenhouse threshold.

For uncertainties in density measurements, we propagate normally distributed errors of mass measurements assuming $\sigma_\mathrm{M_\mathrm{P}} = \SI{10}{\percent}$, as expected for \plato.
As can be seen in Fig.~\ref{fig:plato_fgrid}, the detectability is enhanced when radius constraints can be augmented with mass measurements: At unchanged sample size, the difference in Bayesian evidence can be up to an order of magnitude larger.
Consequently, we achieve a statistically significant detection with smaller samples or lower fractions $f_\mathrm{rgh}$.
A density-based survey of 100 targets is roughly equivalent to a radius-based survey of 500 targets.
At $N=100$, pure radius measurements require $f_\mathrm{rgh} \gtrsim 0.5$ whereas bulk density measurements enable a detection from $f_\mathrm{rgh} \gtrsim 0.2$.

\subsubsection{Spectral type of target stars}
